Component response rate variation underlies the stability of highly complex finite systems

### 2020-03-23 notebook/ms.Rmd
Correct the reference to figures in the introduction

Randomly assembled complex systems can be represented as large square matrices ($\mathbf{M}$) with $S$ components (e.g., networks of species [@Allesina2012] or banks [@Haldane2011]). One element of such a matrix, $M_{ij}$, defines how component $j$ affects component $i$ in the system at a point of equilibrium [@Allesina2012]. Off-diagonal elements ($i \neq j$) therefore define interactions between components, while diagonal elements ($i = j$) define component self-regulation (e.g., carrying capacity in ecological communities). Traditionally, off-diagonal elements are assigned non-zero values with a probability $C$, which are sampled from a distribution with variance $\sigma^{2}$; diagonal elements are set to $-1$ [@May1972; @Allesina2012; @Allesina2015]. Local system stability is assessed using eigenanalysis on $\mathbf{M}$, with the system being stable if the real parts of all eigenvalues ($\lambda$), and therefore the leading eigenvalue ($\lambda_{max}$), are negative ($\Re(\lambda_{max}) < 0$) [@May1972; @Allesina2012]. In a large system (high $S$), eigenvalues are distributed uniformly [@Tao2010] within a circle centred at $\Re = -d$ ($-d$ is the mean value of diagonal elements) and $\Im = 0$, with a radius of $\sigma\sqrt{SC}$ [@May1972; @Allesina2012; @Allesina2015] (Figs 1a and 2a). Local stability of randomly assembled systems therefore becomes increasingly unlikely as $S$, $C$, and $\sigma$ increase.

>>>>

Randomly assembled complex systems can be represented as large square matrices ($\mathbf{M}$) with $S$ components (e.g., networks of species [@Allesina2012] or banks [@Haldane2011]). One element of such a matrix, $M_{ij}$, defines how component $j$ affects component $i$ in the system at a point of equilibrium [@Allesina2012]. Off-diagonal elements ($i \neq j$) therefore define interactions between components, while diagonal elements ($i = j$) define component self-regulation (e.g., carrying capacity in ecological communities). Traditionally, off-diagonal elements are assigned non-zero values with a probability $C$, which are sampled from a distribution with variance $\sigma^{2}$; diagonal elements are set to $-1$ [@May1972; @Allesina2012; @Allesina2015]. Local system stability is assessed using eigenanalysis on $\mathbf{M}$, with the system being stable if the real parts of all eigenvalues ($\lambda$), and therefore the leading eigenvalue ($\lambda_{max}$), are negative ($\Re(\lambda_{max}) < 0$) [@May1972; @Allesina2012]. In a large system (high $S$), eigenvalues are distributed uniformly [@Tao2010] within a circle centred at $\Re = -d$ ($-d$ is the mean value of diagonal elements) and $\Im = 0$, with a radius of $\sigma\sqrt{SC}$ [@May1972; @Allesina2012; @Allesina2015] (Fig. 1a). Local stability of randomly assembled systems therefore becomes increasingly unlikely as $S$, $C$, and $\sigma$ increase.
